---
title: 'Simulate Collusion: Application Examples for Cartel Simulation based on stochastic interest rates'
geometry: margin=1cm
output:
  html_document:
    df_print: paged
  word_document: default
---

Set knitr Options
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy=TRUE, tidy.opts = list(width.cutoff=80))
```

Clear Environment
```{r}
rm(list = ls())
```

Load Packages
```{r include=FALSE}
library(dplyr)
library(tidyr)
library(psych)
library(ggplot2)
library(ggfortify) 
library(forecast)
library(eha) # function phreg()
library(stargazer)
library(simcolr)
```

Set Seed for Reproducibility
```{r}
set.seed(123)
```

### Read in Data
```{r}
# Baseline Model 1 with default parameters.
sim_list <- sim_col_r()

# Model I in Bellert, Günster (2025)
# sim_list <- sim_col_r(model = 1, periods = 1000, n_industries = 300, r_min = 0.001, r_max = 0.3, n_firms_min = 2, n_firms_max = 100, alpha = 500) 
cartels_duration <- get_durations(sim_list$cartels_detected, sim_list$cartels_undetected, sim_list$interest_r, sim_list$deltas, sim_list$parms, model=1)
cartels_duration <- data.frame(cartels_duration)
```

### Add Nonlinear Interdependencies between Variables
```{r}
cartels_duration <- add_nonlinears(cartels_duration, model=1)
```

###  Plot for ICC and Discount Factor of 5 Example Industries
```{r}
set.seed(123)
n_firms <- 4
gamma <- 0.8
theta <- 1
sigma_all <- 0.25
sigma_t <- 1 - (1-sigma_all)^(1/200)
struc <- 1

r_min <- 0.001
r_max <- 0.3

sim_list_M1 <- sim_col_r(model = 1,n_firms_min = 4, n_firms_max = 4, n_industries = 5, sigma = 0.25, gamma = 0.8, theta = 1, struc = 1)
sim_list_M3_1 <- sim_col_r(model = 3,n_firms_min = 4, n_firms_max = 4, n_industries = 5, sigma = 0.25, gamma = 0.8, theta = 1, struc = 1)
sim_list_M3_0 <- sim_col_r(model = 3,n_firms_min = 4, n_firms_max = 4, n_industries = 5, sigma = 0.25, gamma = 0.8, theta = 0, struc = 1)
x <- sim_list_M3_1$ICC
x <- data.frame(x)
df <- cbind(sim_list_M1$ICC[,1,1], sim_list_M3_1$ICC[, 1, 1], sim_list_M3_0$ICC[, 1, 1], sim_list_M3_1$deltas[,,1])
df <- data.frame(df)
sim <- ts(df)
colnames(sim) <- c("ICC MI, II", "ICC MIII (no leniency)", "ICC MIII (full leniency)", paste("Industry", 1:ncol(sim_list_M3_0$deltas[,,1])))
pallete <- c('blue4', 'blue', 'red', 'lightcoral', 'aquamarine3', 'cyan4', 'brown', 'orange')
y_axis <- c(0.725, 0.875) # for singular picture
autoplot(sim) +
 ylim(y_axis) +
  xlab("Time") +
  ylab("") +
  scale_colour_manual(values=pallete) +
  theme(legend.title = element_blank())

```

### Plot Cartel Time Series
```{r}
c_det <- rowSums(sim_list$cartels_detected)/(dim(sim_list$cartels_detected)[2] * dim(sim_list$cartels_detected)[3]) # number of detected cartels / number of industries
c_pop <- rowSums(sim_list$cartels_population)/(dim(sim_list$cartels_population)[2] * dim(sim_list$cartels_population)[3]) # number of cartels / number of industries
sim_cartels <- ts(data = cbind(c_pop, c_det))
colnames(sim_cartels) <- c("Population", "Sample")
pallete <- c('blue', 'red')

autoplot(sim_cartels*100) +
  xlab("Time") +
  ylab("Percentage of cartels") +
  ggtitle("Percentage of Cartels of all Industries over Time") +
  scale_colour_manual(values=pallete) + 
  theme(legend.title = element_blank())

```

### Summary Statistics
```{r}
describe(cartels_duration)
```

### Correlations
```{r}
df_cor <-  Filter(function(x) sd(x) != 0, cartels_duration)
df_cor <- select(df_cor, -c(parm_id, industry, cartel, lduration, nfirms_sigma, mean_delta))
cor(df_cor)
```
### Mean Comparison Tests for Sumstats
```{r}
t.test(duration ~ detected, data=cartels_duration, var.equal = FALSE)
t.test(n_firms ~ detected, data=cartels_duration, var.equal = FALSE)
t.test(sigma ~ detected, data=cartels_duration, var.equal = FALSE)
```

### Linear Regression
```{r}
reg <- lm(lduration ~ start + n_firms + sigma + mean_r + var_r, data = cartels_duration)
summary(reg)
```

### Hazard Rate Estimation
```{r}
periods <- dim(sim_list$cartels_population)[1]
data_pop <- cartels_duration
data_sample <- data_pop[data_pop$detected==1,]
data_undetect <- data_pop[data_pop$detected==0,]

data_pop$dead <- ifelse(data_pop$end < periods, 1, 0)
data_sample$dead <- ifelse(data_sample$end < periods, 1, 0)
data_undetect$dead <- ifelse(data_undetect$end < periods, 1, 0)

hazC <- phreg(Surv(duration, dead) ~ start + n_firms + sigma + mean_r + var_r, data = data_pop,dist='weibull')
hazS <- phreg(Surv(duration, detected) ~ start + n_firms + sigma + mean_r + var_r, data = data_sample,dist='weibull')
hazU <- phreg(Surv(duration, dead) ~ start + n_firms + sigma + mean_r + var_r, data = data_undetect,dist='weibull')

stargazer(hazS, hazU, hazC, 
          title="HR Regression for Cartel Duration on Model I",
          type="text",
          column.labels = c("HRSample", "HRUndetect", "HRCartels"),
          df=FALSE, digits=3)
```

### Future Research: Create Paneldata

```{r}
df_panel <- get_paneldata(sim_list$cartels_population, sim_list$cartels_detected, sim_list$parms, sim_list$interest_r, sim_list$sigmas)
```

